%-------------------------
% Resume in Latex
% Author : Dilip Teja
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------
% C3 AI %
\documentclass[letterpaper,10.9pt]{article}
\usepackage[T1]{fontenc}
\fontfamily{Georgia}\selectfont
\fontseries{m}\selectfont

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{xcolor}
\input{glyphtounicode}

\renewcommand{\bfseries}{\fontseries{b}\selectfont}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.55in}
\addtolength{\textheight}{1.0in}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \scshape\raggedright\small\textbf
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeEducationheading}[4]{
\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \hspace{-1pt}\textbf{ \small #1} & \textbf{\small #2} \\
      \textit{\small #3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeWorkheading}[4]{
\item
    \begin{tabular*}{1.0\textwidth}{l@{\extracolsep{\fill}}r}  
      \textbf{ \small #1} | {\small #2} | {\small #3} & {\small \textbf{#4}} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeskill}[2]{
\item 
      \textbf{ \small #1} \small : {\small #2}  \vspace{-5pt}\\
}

\newcommand{\resumeProjectHeading}[3]{
    \vspace{-2pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      {\small #1}  {\small #2} | {\small #3}\\
    \end{tabular*}\vspace{-5pt}
}

\usepackage{calc} % added
\newcommand{\resumeSubSubheadingLeft}[2]{% % added
\begin{description}[leftmargin=!,labelwidth=\widthof{\small\bfseries #1}]
    \item[\small #1]{\small  #2} \vspace{-7pt}
\end{description}
}


\newcommand{\resumeSubSubheading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{#1} & \textit{#2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-7pt}}
\usepackage[T1]{fontenc}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

%-----------Introduction-----------
\begin{center}
    {\huge \textbf{\textsc{DILIP TEJA}} } \\
    {Pittsburgh, PA}  ~|~
            \faPhoneSquare\ +1-412-330-0823 ~|~
    \href{mailto:tejadilip23898@gmail.com} {\faEnvelopeSquare\ \color{teal}  tejadilip23898@gmail.com} ~|~
    \href{https://www.linkedin.com/in/dilipteja/}{\faLinkedin\ \color{teal} \underline{dilipteja}} ~|~
    \href{https://github.com/dilipteja1}{\faGithubSquare\ \color{teal} \underline{dilipteja1}}
    \vspace{-7pt}
\end{center}

 %-----------EXPERIENCE-----------
\section{WORK EXPERIENCE}
    \resumeSubHeadingListStart

        %MSA experience
        \resumeWorkheading{Software Engineer Co-op}{\color{teal}\href{https://us.msasafety.com/}{\textbf{MSA - The Safety Company}}}{Cranberry, PA}{Jan 2024 -- Apr 2024}
        \resumeItemListStart
            \resumeItem{Architected and deployed a scalable server-side solution using \textbf{WebSockets} and \textbf{Threading}, enabling real-time monitoring of connected plugins, slashing connection latency by over 60 seconds.}
            \resumeItem{Restructured client-side components into \textbf{back-end}, enhancing integration efficiency by 33\% across five projects.}
            \resumeItem{Resolved 3 high-priority bugs along with comprehensive test cases in a dynamic Agile environment, utilizing \textbf{DevOps} tools to improve system reliability.}
        \resumeItemListEnd     
        
        %Qualcomm experience
        \resumeWorkheading
            {Software Engineer}{\color{teal}\href{https://www.qualcomm.com/}{\textbf{Qualcomm}}}{Hyderabad, India}{Jun 2020 -- Dec 2022}
      		\resumeItemListStart
                    \resumeItem{Led design and development of robust change-based test engine for IoT products to curate test suites dynamically, based on code deltas in new builds, optimizing run time by over 70\% for every incoming build. }
                    \resumeItem{Engineered an end-to-end full-stack web application\textit{(full ownership)} streamlining hardware inventory management, and real-time reports generation, reducing company expenses by more than \textbf{\$100k} annually.}
                    \resumeItem{Implemented \textbf{RESTful APIs} in Python for seamless CRUD operations on \textbf{MongoDB} suites, achieving a 35\% boost in code coverage.}
                    \resumeItem{Collaborated with cross-functional teams and enabled API Integration process to 5 different IoT components.}
                    \resumeItem{Eliminated false positives and devised new scenarios as part of \textbf{Linux Kernel} automation, improving overall QA quality by 18\% and pioneered structured and ever-growing documentation.}
                    \resumeItem{Conducted 10+ knowledge-sharing sessions on \textbf{Python, Design Patterns, and Software Design}, fostering team expertise and promoting best practices across projects.}
      		\resumeItemListEnd
        
        %Qualcomm internship experience
        \resumeWorkheading
        {Software Engineer Intern}{\href{https://www.qualcomm.com/}{\color{teal}\textbf{Qualcomm}}}{Hyderabad, India}{Apr 2019 -- Jun 2019}    
            \resumeItemListStart
                \resumeItem{Developed a tool to schedule automation suites execution during off-peak hours and paired it with an admin-driven \textbf{Flask} dashboard for visualization of results, optimizing hardware utilization by 50\%.}
            \resumeItemListEnd
        % \resumeWorkheading
        % {Machine Learning Intern}{IISc, Bangalore}{Bangalore, India}{Apr 2018 -- Jun 2018}     
        %     \resumeItemListStart
        %         \resumeItem{Experimented ML techniques like data augmentation and fine-tuning existing models.}
        %     \resumeItemListEnd   
    \resumeSubHeadingListEnd
%-----------PROJECTS-----------
\section{PROJECTS}
    \resumeSubHeadingListStart
            \resumeProjectHeading
             {\textbf{Group Chat System}}{\href{https://github.com/CS2510-Distributed-Systems/Advanced-Group-Chat-System}{\faGithub}}{\emph{Go, gRPC, Protocol Buffers, docker}}
                \resumeItemListStart
                        \resumeItem{Created a distributed chat system with 5 servers and multiple clients featuring availability, synchronization, eventual consistency, replication, fault/partition tolerance.}
                        \resumeItem{Incorporated Two-phase locking, Vector timestamps of partial ordering, Bidirectional Streaming.}
              		\resumeItemListEnd
            \resumeProjectHeading
             {\textbf{De-identification of PHI in EHR}}{\href{https://github.com/dilipteja1/de-identification-of-PHI-in-Electronics-Health-Records.-/tree/main}{\faGithub}}{\emph{Pytorch, LLM, Hugging Face}}
          		    \resumeItemListStart
                            \resumeItem{Performed transfer learning on pre-trained large language models such as \textbf{BERT, LLaMA} to de-identify protected health information(PHI) in electronic health records(EHR) dataset.}
                            \resumeItem{Leveraged \textbf{Tokenization, BIO encoding} and other NLP techniques to achieve an average F1 score of 0.98.}
                        \resumeItemListEnd
            
    \resumeSubHeadingListEnd

  %-----------SKILLS-----------
\section{TECHNICAL SKILLS}
    \resumeSubHeadingListStart
        \resumeskill{Programming Languages}{Python, Go, JavaScript, TypeScript, C++, SQL, HTML}
        \resumeskill{Technologies \& libraries}{React, Redux, Django, Flask, Node, Express, Next, JQuery, TailwindCSS, gRPC,  Protocol Buffers, REST API, Git, Github, Docker, Prometheus, Grafana, Pytorch, Google Colab, Windows, Linux }
        \resumeskill{Database \& Cloud Services}{MySQL, PostgreSQL, MongoDB, AWS}
        \resumeskill{Concepts}{JIRA, Agile, CI/CD, Software Development Life Cycle(SDLC), Front-end web development}
    \resumeSubHeadingListEnd
    
  %-----------EDUCATION-----------
\section{EDUCATION} 
    \resumeSubHeadingListStart
        % masters education
        \resumeEducationheading
            {University of Pittsburgh}{Jan 2023 -- Apr 2025}
            {Master of Science in Computer Science}{Pittsburgh, PA}
            \resumeItem{\textbf{Coursework:} Distributed Systems, Advanced Algorithms, Databases, AI, Machine Learning, Natural language processing} 
        \resumeEducationheading
            {National Institute of Technology, Warangal}{Jun 2016 -- May 2020}
            {Bachelor of Technology in Electronics and Communication }{Warangal, India}
            \resumeItem{\textbf{Relevant Coursework:} Data Structures and Algorithms, Computer Networks,Object oriented Programming, Probability \& Statistics}
    \resumeSubHeadingListEnd


%-----------CO-CURRICULARS-----------
\section{AWARDS AND ACHIEVEMENTS}
\resumeSubHeadingListStart
    \resumeItemListStart      
        	\resumeItem{Recipient of \textbf{Orion Insta} and \textbf{Top Executor Awards} from Senior Director at Qualcomm for contribution and efforts.}
            
             \resumeItem{Secured \textbf{second place }in Microsoft's Code.Fun.Do Hackathon among 50+ teams across university.}
             
            \resumeItem{Achieved \textbf{All India Rank 602} in IIT-JEE  Mains among over 1.2 million candidates. }

            \resumeItem{Led university badminton team as captain for 2 consecutive years, securing top positions in inter-university tournaments.}
    \resumeItemListEnd
\resumeSubHeadingListEnd
            
%   \resumeItemListEnd
% \resumeSubHeadingListEnd
  
%   %-----------LEADERSHIP-----------
% \section{LEADERSHIP}
%     \resumeSubHeadingListStart        
%         \resumeSubSubheading       
%             {\textbf{Batch Representative}}{Aug 2019 -- Mar 2020}
%             \resumeItemListStart      
%                 \resumeItem{Represented ECE Class of 2020 in Department UG Council and other department events.}
%             \resumeItemListEnd 
%         \resumeSubSubheading   
%             {\textbf{Sponsorship and Public Relations Sub-Coordinator}}{Aug 2018 -- Mar 2019}
%             \resumeItemListStart      
%                 \resumeItem{Organized university's cultural festival 'Spring Spree' by communicating and gathering sponsors.}
%             \resumeItemListEnd
%     \resumeSubHeadingListEnd


\end{document}
